title_uniform

### 2022-04-20 inst/examples/holder.Rmd
ok

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$holder))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/holder_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$holder))` / `r nrow(df)` (`r round(100*mean(!is.na(df$holder)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$holder))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$holder)), 1)`%)

>>>>

* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

### 2022-04-20 inst/examples/subject_topic.Rmd
ok

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$subject_topic))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/subject_topic_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$subject_topic))` / `r nrow(df)` (`r round(100*mean(!is.na(df$subject_topic)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)

>>>>

* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

### 2022-04-20 inst/examples/successor.Rmd
ok

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$successor))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/successor_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$successor))` / `r nrow(df)` (`r round(100*mean(!is.na(df$successor)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$successor))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$successor)), 1)`%)

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "successor", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$successor)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, field, ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique entries:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df[[field]])
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-04-20 inst/examples/title_uniform.Rmd
ok

 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)

>>>>

* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
